---
title: "Assignment3"
author: "RF"
date: "3/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Multivariate linear models

In this assignment you will investigate the relation between different aspects of IQ and symptom severity in ASD (as measured by ADOS). The assignment is meant to make you practice on linear models, multiple predictors and interactions.

The data you will use is the outcome of the psychological testing of the children you analyzed in methods 3.
Data: https://www.dropbox.com/s/hom2qnmp9hyfwmu/Assignment3Data.csv?dl=0
The data consists of ChildID, gender, age, diagnosis (ASD), symptom severity (ADOS), several aspects of IQ (NonVerbal/Perceptual,Verbal,Social) and the visit at which the tests were administered. The questions should be answered by focusing on visit 1.

The questions you will have to answer are:

1. Assess the relation between symptom severity and IQ (focus on visit 1 and children with ASD) and report the model, a plot of the model, a couple of lines describing the quality of the model and interpreting the results. 
P.S. Should you scale? 
P.P.S. Don't forget to motivate your priors. 
P.P.P.S. At least one plot for results and a plot for quality of each model (here and in the next questions) would be appreciated.
1.1. Verbal IQ and ADOS
1.2. Non Verbal IQ and ADOS
1.3. Social IQ and ADOS

```{r}
pacman::p_load(ggplot2, rethinking, gridExtra, dplyr)

### ---------------- ###
### PRELIMINARY WORK ###
### ---------------- ###

d = read.csv("Assignment3Data.csv")
d_d= subset(d, Visit == 1 & ASD == 1)
d1 = d_d[complete.cases(d_d),]

## Visualize
# Nonverbal
a = ggplot(d1, aes(ADOS, NonVerbalIQ)) +
  geom_point()

# Verbal
b = ggplot(d1, aes(ADOS, VerbalIQ)) +
  geom_point()

# Social
c = ggplot(d1, aes(ADOS, SocialIQ)) +
  geom_point()

gridExtra::grid.arrange(a,b,c)

# Find the ADOS = 0 kid
d1[which(d1$ADOS == 0), ]

# Plot the TD kids
d_d= subset(d, Visit == 1 & ASD == 0)
d2 = d_d[complete.cases(d_d),]
# Nonverbal
a = ggplot(d2, aes(ADOS, NonVerbalIQ)) +
  geom_point()

# Verbal
b = ggplot(d2, aes(ADOS, VerbalIQ)) +
  geom_point()

# Social
c = ggplot(d2, aes(ADOS, SocialIQ)) +
  geom_point()

gridExtra::grid.arrange(a,b,c)

# Exclude the guy who scores 0 on ADOS but has ASD
d1 = subset(d1, ADOS > 0)

# Do centering and standardizing to scale and because of correlations
# Centering
d1$ADOS.c = d1$ADOS - mean(d1$ADOS)
d1$VerbalIQ.c = d1$VerbalIQ - mean(d1$VerbalIQ)
d1$NonVerbalIQ.c = d1$NonVerbalIQ - mean(d1$NonVerbalIQ)
d1$SocialIQ.c = d1$SocialIQ - mean(d1$SocialIQ)

# Standardize
d1$NonVerbalIQ.s <- (d1$NonVerbalIQ.c-mean(d1$NonVerbalIQ.c))/sd(d1$NonVerbalIQ.c)
d1$VerbalIQ.s <- (d1$VerbalIQ.c-mean(d1$VerbalIQ.c))/sd(d1$VerbalIQ.c)
d1$SocialIQ.s <- (d1$SocialIQ.c-mean(d1$SocialIQ.c))/sd(d1$SocialIQ.c)
d1$ADOS.s <- (d1$ADOS.c-mean(d1$ADOS.c))/sd(d1$ADOS.c)

d1$ADOS.s = scale(d1$ADOS)

# Info for the priors
mean(d1$VerbalIQ)
mean(d1$NonVerbalIQ)
mean(d1$SocialIQ)
mean(d1$ADOS)
sd(d1$VerbalIQ)
sd(d1$NonVerbalIQ)
sd(d1$SocialIQ)
sd(d1$ADOS)
```



```{r}
### ----------------------- ###
### BUILD MODELS FOR 3 IQ's ###
### ----------------------- ###

# The model for verbal IQ
V_model <- map(
  alist(
  ADOS.s ~ dnorm(mu,sigma), #likelihood
    mu <- a + b*VerbalIQ.s, #linear model
    a ~ dnorm(0, 5), #ADOS prior, whats the expected Verbal IQ when ADOS is 0?
    b ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = d1
)
precis(V_model, corr = T)
precis_plot(precis(V_model, corr = T))

#Plot results
#Create many different posteriors
post <- extract.samples(V_model) 

#a function that calculates mu for a specific x-value
mu.link <- function(x) post$a + post$b*x
#Make a list of numbers for VerbalIQ
Predictor_sequence <- seq(from=min(d1$VerbalIQ.s), to=max(d1$VerbalIQ.s) , by=0.1 )
#Calculate the mu for each of the verbalIQ's
mu <- sapply( Predictor_sequence , mu.link )
#What's the mean mu?
mu_mean <- apply( mu , 2 , mean )
#High Probability Density Intervals
mu_HPDI <- apply( mu , 2 , HPDI , prob=0.89 )

#Simulate mean outputs
Output_sim <- sim( V_model , data=list(VerbalIQ.s=Predictor_sequence) )

#Create percentile interval - the 89% most likely area
Output_PI <- apply( Output_sim , 2 , PI , prob=0.89 )

#Plot the raw data
plot( ADOS.s ~ VerbalIQ.s , d1 , col=col.alpha(rangi2,0.5) )
# the MAP model line
lines( Predictor_sequence , mu_mean )
# draw high probability density intervals for line
shade( mu_HPDI , Predictor_sequence ) 
# draw PI region for simulated heights
shade( Output_PI , Predictor_sequence )


###ASSESSING QUALITY:
dens(Output_sim, col = "red", xlim = c(-4, 4), ylim = c(0,0.6),  xlab = "ADOS")
par(new=TRUE)
dens(d1$ADOS.s, xlim = c(-4, 4), ylim = c(0,0.6), xlab = "ADOS")

#dens(mu - d1$ADOS.s)
```


```{r}

#### ------- ###
# The model for nonverbal IQ
nV_model <- map(
  alist(
    ADOS.s ~ dnorm(mu,sigma), #likelihood
    mu <- a + b*NonVerbalIQ.s, #linear model
    a ~ dnorm(0, 5), #NonVerbalIQ prior, whats the expected Verbal IQ when ADOS is 0?
    b ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = d1
)

precis(nV_model, corr = T)
precis_plot(precis(nV_model, corr = T))

#Plot results
#Create many different posteriors
post <- extract.samples(nV_model) 

#a function that calculates mu for a specific x-value
mu.link <- function(x) post$a + post$b*x
#Make a list of numbers for VerbalIQ
Predictor_sequence <- seq(from=min(d1$NonVerbalIQ.s), to=max(d1$NonVerbalIQ.s) , by=0.1 )
#Calculate the mu for each of the verbalIQ's
mu <- sapply( Predictor_sequence , mu.link )
#What's the mean mu?
mu_mean <- apply( mu , 2 , mean )
#High Probability Density Intervals
mu_HPDI <- apply( mu , 2 , HPDI , prob=0.89 )

#Simulate mean outputs
Output_sim <- sim( nV_model , data=list(NonVerbalIQ.s=Predictor_sequence) )

#Create percentile interval - the 89% most likely area
Output_PI <- apply( Output_sim , 2 , PI , prob=0.89 )

#Plot the raw data
plot( ADOS.s ~ NonVerbalIQ.s , d1 , col=col.alpha(rangi2,0.5) )
# the MAP model line
lines( Predictor_sequence , mu_mean )
# draw high probability density intervals for line
shade( mu_HPDI , Predictor_sequence ) 
# draw PI region for simulated heights
shade( Output_PI , Predictor_sequence )


###ASSESSING QUALITY:
dens(Output_sim, col = "red", xlim = c(-4, 4), ylim = c(0,0.6),  xlab = "ADOS")
par(new=TRUE)
dens(d1$ADOS.s, xlim = c(-4, 4), ylim = c(0,0.6), xlab = "ADOS")

```

```{r}

# The model for social IQ
S_model <- map(
  alist(
    ADOS.s ~ dnorm(mu,sigma), #likelihood
    mu <- a + b*SocialIQ.s, #linear model
    a ~ dnorm(0, 5), #SocialIQ prior, whats the expected Verbal IQ when ADOS is 0?
    b ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = d1
)
precis(S_model, corr = T)
precis_plot(precis(S_model, corr = T))

#Plot results
#Create many different posteriors
post <- extract.samples(S_model) 

#a function that calculates mu for a specific x-value
mu.link <- function(x) post$a + post$b*x
#Make a list of numbers for VerbalIQ
Predictor_sequence <- seq(from=min(d1$SocialIQ.s), to=max(d1$SocialIQ.s) , by=0.1 )
#Calculate the mu for each of the verbalIQ's
mu <- sapply( Predictor_sequence , mu.link )
#What's the mean mu?
mu_mean <- apply( mu , 2 , mean )
#High Probability Density Intervals
mu_HPDI <- apply( mu , 2 , HPDI , prob=0.89 )

#Simulate mean outputs
Output_sim <- sim( S_model , data=list(SocialIQ.s=Predictor_sequence) )

#Create percentile interval - the 89% most likely area
Output_PI <- apply( Output_sim , 2 , PI , prob=0.89 )

#Plot the raw data
plot( ADOS.s ~ SocialIQ.s , d1 , col=col.alpha(rangi2,0.5) )
# the MAP model line
lines( Predictor_sequence , mu_mean )
# draw high probability density intervals for line
shade( mu_HPDI , Predictor_sequence ) 
# draw PI region for simulated heights
shade( Output_PI , Predictor_sequence )


###ASSESSING QUALITY:
dens(Output_sim, col = "red", xlim = c(-4, 4), ylim = c(0,0.6),  xlab = "ADOS")
par(new=TRUE)
dens(d1$ADOS.s, xlim = c(-4, 4), ylim = c(0,0.6), xlab = "ADOS")


```

```{r}

```


```{r}
### ----------------------------------------------- ###
### QUALITY OF MODELS - PERCENTILE INTERVAL OF MEAN ###
### ----------------------------------------------- ###

# VerbalIQ
# Compute percentile interval of mean
V.seq <- seq( from=-3 , to=30 , length.out=30 )
mu <- link(V_model, data=data.frame(ADOS=V.seq) )
mu.PI <- apply( mu , 2 , PI )
# plot it all
a = plot( VerbalIQ ~ ADOS , data=d1 , col=rangi2 ) + 
  abline( V_model ) +
  shade( mu.PI , V.seq )

# NonVerbalIQ
# Compute percentile interval of mean
nV.seq <- seq( from=-3 , to=40 , length.out=30 )
mu <- link(nV_model, data=data.frame(ADOS=nV.seq) )
mu.PI <- apply( mu , 2 , PI )
# plot it all
b = plot( NonVerbalIQ ~ ADOS , data=d1 , col=rangi2 ) + 
  abline( nV_model ) +
  shade( mu.PI , nV.seq )

# SocialIQ
# Compute percentile interval of mean
S.seq <- seq( from=-3 , to=30 , length.out=150 )
mu <- link(S_model, data=data.frame(ADOS=S.seq) )
mu.PI <- apply( mu , 2 , PI )
# plot it all
c = plot( SocialIQ ~ ADOS , data=d1 , col=rangi2 ) + 
  abline( S_model ) +
  shade( mu.PI , S.seq )

### ---------------------------------- ###
### SECOND QUALITY CHECK - UNCERTANITY ###
### ---------------------------------- ###

# Need to add uncertainty on the plot, get samples of posterior distribution
V_post = extract.samples(V_model)
nV_post = extract.samples(nV_model)
S_post = extract.samples(S_model)

# Same for all
N = 33 #all people
dN = d1[1:N,]

# Verbal IQ
V <- map(
  alist(
    VerbalIQ ~ dnorm(mu,sigma), #likelihood
    mu <- a + b*ADOS, #linear model
    a ~ dnorm(18, 7.6), #VerbalIQ prior, whats the expected Verbal IQ when ADOS is 0?
    b ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = dN
)

# NonVerbal IQ
nV <- map(
  alist(
    NonVerbalIQ ~ dnorm(mu,sigma), #likelihood
    mu <- a + b*ADOS, #linear model
    a ~ dnorm(26.8, 5.5), #NonVerbalIQ prior, whats the expected Verbal IQ when ADOS is 0?
    b ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = dN
)

# The model for social IQ
S <- map(
  alist(
    SocialIQ ~ dnorm(mu,sigma), #likelihood
    mu <- a + b*ADOS, #linear model
    a ~ dnorm(77.2, 10.4), #SocialIQ prior, whats the expected Verbal IQ when ADOS is 0?
    b ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = dN
)

# Now plot 20 of these lines to see the uncertainty
## Extract the 20 samples
V_post = extract.samples(V, n=20)
nV_post = extract.samples(nV, n=20)
S_post = extract.samples(S, n=20)

## Display raw data and sample size
u_V = plot(dN$ADOS , dN$VerbalIQ ,
     xlim=range(d1$ADOS) , ylim=range(d1$VerbalIQ) ,
     col=rangi2 , xlab="ADOS" , ylab="Verbal IQ" ) + 
  mtext(concat("N = ",N)) + 
  for ( i in 1:20 ) abline(a= V_post$a[i] , b= V_post$b[i] , col=col.alpha("black",0.3) )

u_nV = plot(dN$ADOS , dN$NonVerbalIQ ,
     xlim=range(d1$ADOS) , ylim=range(d1$NonVerbalIQ) ,
     col=rangi2 , xlab="ADOS" , ylab="Nonverbal IQ" ) + 
  mtext(concat("N = ",N)) + 
  for ( i in 1:20 ) abline(a= nV_post$a[i] , b= nV_post$b[i] , col=col.alpha("black",0.3) )

u_S = plot(dN$ADOS , dN$SocialIQ ,
     xlim=range(d1$ADOS) , ylim=range(d1$SocialIQ) ,
     col=rangi2 , xlab="ADOS" , ylab="Social IQ" ) + 
  mtext(concat("N = ",N)) + 
  for ( i in 1:20 ) abline(a= S_post$a[i] , b= S_post$b[i] , col=col.alpha("black",0.3) )

```


2. Do the different aspects of IQ account for different portions of the variance in ADOS? 
2.1. Does it make sense to have all IQ measures in the same model? First write a few lines answering the question and motivating your answer, including a discussion as to what happens when you put all of them in the same model. Then build a model following your answer. If your answer is "no", you are not free, you still have to answer: are there alternative ways of answering the question?
2.2. Build the model, assess its quality, write a few lines interpreting the results.

```{r}
# Let's do a multiple regression
# Run it again with all of them - this time scaled variables because easier to compare
model.all.s <- map(
  alist(
    ADOS.s ~ dnorm(mu,sigma), #likelihood
    mu <- a + bNon*NonVerbalIQ.s + bVer*VerbalIQ.s + bSoc*SocialIQ.s, #linear model
    a ~ dnorm(0, 5), #VerbalIQ prior, whats the expected Verbal IQ when ADOS is 0?
    bNon ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    bVer ~ dnorm(0, 5),
    bSoc ~ dnorm(0, 5),
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = d1
)
precis(model.all.s, corr = T)
precis_plot(precis(model.all.s, corr = T))

#Predictive Posterior check
Output_sim <- sim( model.all.s, data=d1)

#Plotting predicted and observed distributions
dens(Output_sim, col = "red", xlim = c(-4, 4), ylim = c(0,0.6),  xlab = "ADOS")
par(new=TRUE)
dens(d1$ADOS.s, xlim = c(-4, 4), ylim = c(0,0.6), xlab = "ADOS")
```
```{r}
# Without V
model.0V.s <- map(
  alist(
    ADOS.s ~ dnorm(mu,sigma), #likelihood
    mu <- a + bNon*NonVerbalIQ.s + bSoc*SocialIQ.s, #linear model
    a ~ dnorm(0, 5), #VerbalIQ prior, whats the expected Verbal IQ when ADOS is 0?
    bNon ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    bSoc ~ dnorm(0, 5),
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = d1
)
precis(model.0V.s, corr = T)
precis_plot(precis(model.0V.s, corr = T))

#Predictive Posterior check
Output_sim <- sim( model.0V.s, data=d1)

#Plotting predicted and observed distributions
dens(Output_sim, col = "red", xlim = c(-4, 4), ylim = c(0,0.6),  xlab = "ADOS")
par(new=TRUE)
dens(d1$ADOS.s, xlim = c(-4, 4), ylim = c(0,0.6), xlab = "ADOS")
```


```{r}
# -------------# 

# Without nV
model.0nV.s <- map(
  alist(
    ADOS.s ~ dnorm(mu,sigma), #likelihood
    mu <- a + bVer*VerbalIQ.s + bSoc*SocialIQ.s, #linear model
    a ~ dnorm(0, 5), #VerbalIQ prior, whats the expected Verbal IQ when ADOS is 0?
    bVer ~ dnorm(0, 5),
    bSoc ~ dnorm(0, 5),
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = d1
)
precis(model.0nV.s, corr = T)
precis_plot(precis(model.0nV.s, corr = T))


# Without S
model.0S.s <- map(
  alist(
    ADOS.s ~ dnorm(mu,sigma), #likelihood
    mu <- a + bNon*NonVerbalIQ.s + bVer*VerbalIQ.s, #linear model
    a ~ dnorm(0, 5), #VerbalIQ prior, whats the expected Verbal IQ when ADOS is 0?
    bNon ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    bVer ~ dnorm(0, 5),
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = d1
)
precis(model.0S.s, corr = T)
precis_plot(precis(model.0S.s, corr = T))

# As expected from the all-in models - doesn't help to have all of them?
# can u only say that when they overlap with 0?

### ----------------------------------------------- ###
### QUALITY OF MODEL - PERCENTILE INTERVAL OF MEAN ###
### ----------------------------------------------- ###

precis_plot(precis(model.all.s, corr = T))

pairs( ~ ADOS.s + NonVerbalIQ.s + VerbalIQ.s + SocialIQ.s ,
       data=d1 , col=rangi2 )

cor(d1$NonVerbalIQ.s, d1$VerbalIQ.s)
cor(d1$NonVerbalIQ.s, d1$SocialIQ.s)
cor(d1$VerbalIQ.s, d1$SocialIQ.s)


```


3. Let's now include also the TD children. Does it make sense to ask whether IQ and ADOS are related? Motivate your answer. In any case, if you wanted to build a model to answer that question, which model would you build? Run the model, assess its quality, write a few lines interpreting the results.

```{r}
d = read.csv("Assignment3Data.csv")
d_d= subset(d, Visit == 1)
d1 = d_d[complete.cases(d_d),]

# Do centering and standardizing to scale and because of correlations
# Centering
d1$ADOS.c = d1$ADOS - mean(d1$ADOS)
d1$VerbalIQ.c = d1$VerbalIQ - mean(d1$VerbalIQ)
d1$NonVerbalIQ.c = d1$NonVerbalIQ - mean(d1$NonVerbalIQ)
d1$SocialIQ.c = d1$SocialIQ - mean(d1$SocialIQ)

# Standardize
d1$NonVerbalIQ.s <- (d1$NonVerbalIQ.c-mean(d1$NonVerbalIQ.c))/sd(d1$NonVerbalIQ.c)
d1$VerbalIQ.s <- (d1$VerbalIQ.c-mean(d1$VerbalIQ.c))/sd(d1$VerbalIQ.c)
d1$SocialIQ.s <- (d1$SocialIQ.c-mean(d1$SocialIQ.c))/sd(d1$SocialIQ.c)
d1$ADOS.s <- (d1$ADOS.c-mean(d1$ADOS.c))/sd(d1$ADOS.c)

# Try to predict ADOS from all kids
model.all.s <- map(
  alist(
    ADOS.s ~ dnorm(mu,sigma), #likelihood
    mu <- a + bNon*NonVerbalIQ.s + bVer*VerbalIQ.s + bSoc*SocialIQ.s, #linear model
    a ~ dnorm(0, 5), #VerbalIQ prior, whats the expected Verbal IQ when ADOS is 0?
    bNon ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    bVer ~ dnorm(0, 5),
    bSoc ~ dnorm(0, 5),
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = d1
)
precis(model.all.s, corr = T)
precis_plot(precis(model.all.s, corr = T))
# Seems like SocialIQ really makes a difference

#Predictive Posterior check
Output_sim <- sim( model.all.s, data=d1)

#Plotting predicted and observed distributions
dens(Output_sim, col = "red", xlim = c(-4, 4), ylim = c(0,1),  xlab = "ADOS")
par(new=TRUE)
dens(d1$ADOS.s, xlim = c(-4, 4), ylim = c(0,1), xlab = "ADOS")
```

```{r}

# Try to predict ADOS from only social IQ
model.S <- map(
  alist(
    ADOS.s ~ dnorm(mu,sigma), #likelihood
    mu <- a + bSoc*SocialIQ.s, #linear model
    a ~ dnorm(0, 5),
    bSoc ~ dnorm(0, 5),
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = d1
)

precis(model.S, corr = T)
precis_plot(precis(model.S, corr = T))
# Seems like SocialIQ really makes a difference

#Predictive Posterior check
Output_sim <- sim( model.S, data=d1)

#Plotting predicted and observed distributions
dens(Output_sim, col = "red", xlim = c(-4, 4), ylim = c(0,1),  xlab = "ADOS")
par(new=TRUE)
dens(d1$ADOS.s, xlim = c(-4, 4), ylim = c(0,1), xlab = "ADOS")
```


4. Let's discuss contents:
4.1. You have three scores for IQ, do they show shared variance? Is that the same in TD and ASD? What does that tell us about IQ?
4.2. You have explored the relation between IQ and ADOS. How do you explain that relation from a cognitive perspective? N.B. You can present alternative hypotheses.

5. Bonus questions: Including measurement errors. 
5.1. Let's assume that ADOS has a measurement error of 1. How would you model that in any of the previous models? 
5.2. We know that IQ has an estimated measurement error of 2.12. How would you include that? 


```{r}
## More ways to add uncertainity for mm 1st question
# Need to add uncertainty on the plot, get samples of posterior distribution
post = extract.samples(model.c)

post[1:5,]

N = 33 #all people
dN = d1[1:N,]
mN <- map(
  alist(
    VerbalIQ ~ dnorm(mu,sigma), #likelihood
    mu <- a + b*ADOS, #linear model
    a ~ dnorm(18, 7.6), #VerbalIQ prior, whats the expected Verbal IQ when ADOS is 0?
    b ~ dnorm(0, 5), #expected change for a unit of 1, 5 means am agnostic
    sigma ~ dunif(0, 50) #sigma prior
  ) ,
  data = dN
)

# Now plot 20 of these lines to see the uncertainty
## Extract the 20 samples
post = extract.samples(mN, n=20)

## Display raw data and sample size
plot(dN$ADOS , dN$VerbalIQ ,
     xlim=range(d1$ADOS) , ylim=range(d1$VerbalIQ) ,
     col=rangi2 , xlab="ADOS" , ylab="Verbal IQ" ) + 
  mtext(concat("N = ",N)) + 
  for ( i in 1:20 ) abline(a=post$a[i] , b=post$b[i] , col=col.alpha("black",0.3) )
## Plot the lines, with transparency

#Run for NonVerbal IQ





#################


#uhm
mu = link(model.c)
str(mu) #values for u, each row is a sample from posterior

# define sequence of weights to compute predictions for
# these values will be on the horizontal axis
ADOS.seq <- seq( from=0 , to=21 , by=1 )
# use link to compute mu
# for each sample from posterior
# and for each weight in weight.seq
mu <- link( model , data = data.frame(weight=ADOS.seq) )
str(mu)

##################


# Get the samples
posterior = extract.samples(model)
plot(posterior)
dens(posterior)

# use link
mu <- link(model)
plot(mu)
dens(mu)

plot(d1$NonVerbalIQ ~ d1$ADOS)
plot(d1$VerbalIQ ~ d1$ADOS)
plot(d1$SocialIQ ~ d1$ADOS)

#sampling actual outcomes
sim = sim(model, data=list(weights))
#sample(p_grid , prob=posterior_RF , size=1e4 , replace=TRUE )

# Sample all possible p's, weigh them with posterior likelihood of each value of p
w <- rbinom( 1e4 , size = 10 , prob = samples)

# Make the histogram
simplehist(w)

#flist = alist( )
```

